---
title: "Review Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
---

```{r include = FALSE}
library(viridis)
library(ggplot2)
library(marmap)
```

# Intro {.sidebar}

This dashboard covers several topics:

* The marmap package
* The viridis package
* Miscellaneous material

GRÁFICO EM DIVERSOS FORMATOS:

* Gráfico Plot 
* Gráfico Plot e COS
* Gráfico Imagem


# Marmap Package

## Column 1

### Florida

```{r echo = FALSE}
data(florida)
plot(florida, image = TRUE, lwd = 0.5, main = "Florida Bathymetry")
```

The [marmap](https://cran.r-project.org/web/packages/marmap/index.html) package provides tools and data for visualizing the ocean floor. Here is an example contour plot of marmap's `florida` dataset.

## Column 2

### Hawaii

```{r echo = FALSE}
data(hawaii)
plot(hawaii, image = TRUE, lwd = 0.5, main = "Hawaii Bathymetry")
```

### Alaska

```{r echo = FALSE}
data(aleutians)
plot(aleutians, image = TRUE, lwd = 0.5, main = "Aleutians Bathymetry")
```


# Viridis Package

## Column 1

### Viridis colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200))
```

### Magma colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "A"))
```

## Column 2

### Inferno colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "B"))
```

### Plasma colors

```{r fig.cap="Maunga Whao, Auckland, NZ"}
image(volcano, col = viridis(200, option = "C"))
```

# Miscellaneous

## Column 1 {data-width=300}

### Bash support

```{r}
x <- rnorm(200)
hist(x)
```

***

This chunk executes bash code.

### Python support

```{r}
riqueza <- c(15,18,22,24,25,30,31,34,37,39,41,45)
area.cate <- rep(c("pequeno", "grande"), each=6)
boxplot(riqueza~area.cate)
```

***

This chunk executes python code.

## Column 2 {data-width=700}

### Tables with Kable 

```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(mtcars[1:5, ], caption = "A knitr kable.")
```

***

It is very easy to make tables with knitr's `kable` function.




-------------------------------------
# Gráfico Plot

## Column 1
    
###  PLOT 1
    
```{r}

x=rnorm(100)
y=rnorm(100)
plot(x,y)

```
   
# Gráfico Plot e COS

## Column 2
    
### Grafico 2
    
```{r}
plot(x,y,xlab="this is the x-axis",ylab="this is the y-axis",main="Plot of X vs Y")
```
    
### Grafico 3

```{r}
x=seq(-pi,pi,length=50)
y=x
f=outer(x,y,function(x,y)cos(y)/(1+x^2))
contour(x,y,f)
```

# Gráfico Imagem

## Column 3
    
### Grafico 4
```{r}
x=seq(-pi,pi,length=50)
y=x
f=outer(x,y,function(x,y)cos(y)/(1+x^2))
contour(x,y,f)
contour(x,y,f,nlevels=45,add=T)
fa=(f-t(f))/2
contour(x,y,fa,nlevels=15)
image(x,y,fa)
```