---
params:
  symbol1: AMZN
  symbol2: GOOG
  symbol3: CSCO
  symbol4: ADBE
  symbol5: AAPL
---

# Introduction

```{r include = FALSE}
library(quantmod)
library(dygraphs)

stock1 <- getSymbols(params$symbol1, auto.assign = FALSE,
                    from = "2019-01-01", end = Sys.Date())
stock2 <- getSymbols(params$symbol2, auto.assign = FALSE,
                    from = "2019-01-01", end = Sys.Date())
stock3 <- getSymbols(params$symbol3, auto.assign = FALSE,
                    from = "2019-01-01", end = Sys.Date())
stock4 <- getSymbols(params$symbol4, auto.assign = FALSE,
                    from = "2019-01-01", end = Sys.Date())
stock5 <- getSymbols(params$symbol5, auto.assign = FALSE,
                    from = "2019-01-01", end = Sys.Date())
```


This report examines the price of the stocks: 
  
* ``r params$symbol1``
* ``r params$symbol2``
* ``r params$symbol3``
* ``r params$symbol4``
* ``r params$symbol5``

It is written in [R Markdown](http://rmarkdown.rstudio.com), an authoring format that enables easy creation of dynamic documents, presentations, and reports from R. R Markdown combines the core syntax of **markdown** (an easy to write plain text format) with embedded **R** code chunks that are run so their output can be included in the final document.

The data comes from [Yahoo finance](http://finance.yahoo.com).

### ``r params$symbol1`` price

```{r echo = FALSE}
dygraph(Cl(stock1))
```

### ``r params$symbol2`` price

```{r echo = FALSE}
dygraph(Cl(stock2))
```

### ``r params$symbol3`` price

```{r echo = FALSE}
dygraph(Cl(stock3))
```

### ``r params$symbol4`` price

```{r echo = FALSE}
dygraph(Cl(stock4))
```

### ``r params$symbol5`` price

```{r echo = FALSE}
dygraph(Cl(stock5))
```